Clinical prediction with localized modeling using similarity-based cohorts: A scoping review

### 2023-08-16 docs/Manuscript/Manuscript.Rmd
include new plot in manuscript + debug use of read_rds

```{r tab:synthesis, echo=FALSE, message=FALSE, warning=FALSE}
tab_synthesis <- read_rds(here::here("tab/synthesis.rds"))
tab_synthesis |> 
  select(-Date) |> 
  # prevent numeric list columns from dominating the horizontal space
  mutate(across(
    c(-Citation, -Cases, -Features),
    ~ str_c(., "\\hspace{6em}")
  )) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:synthesis}",
      "Studies included in the method synthesis,",
      " arranged by the earliest the study is known to have been public."
    )
  )
```

@@

The frequency plot in Figure \ref{fig:} compares the rates at which several methodological elements are invoked in the sample.

```{r fig:methods, fig.align='center', out.width="100%", echo=FALSE}
#| fig.cap =
#| "\\label{fig:methods}
#| Frequency of recurring methodological elements across included studies."
# knitr::include_graphics("../../fig/fig-methods.png")
```

>>>>

```{r tab:synthesis, echo=FALSE, message=FALSE, warning=FALSE}
tab_synthesis <- readr::read_rds(here::here("tab/synthesis.rds"))
tab_synthesis |> 
  select(-Date) |> 
  # prevent numeric list columns from dominating the horizontal space
  mutate(across(
    c(-Citation, -Cases, -Features),
    ~ str_c(., "\\hspace{6em}")
  )) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:synthesis}",
      "Studies included in the method synthesis,",
      " arranged by the earliest the study is known to have been public."
    )
  )
```

@@

The frequency plot in Figure \ref{fig:methods} compares the rates at which several methodological elements are invoked in the sample.

```{r fig:methods, fig.align='center', out.width="100%", echo=FALSE}
#| fig.cap =
#| "\\label{fig:methods}
#| Frequency of recurring methodological elements across included studies."
knitr::include_graphics("../../fig/fig-methods.png")
```
